PANCHANGE_analysis

### 2020-12-17 PANCHANGE_analysis.Rmd
reknitted for figure size

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "Comorbid depression and anxiety",
                             "Depressive disorders",
                             "Anxiety disorders",
                             "Eating disorders",
                             "Obsessive compulsive disorders",
                             "Comorbid psychotic and bipolar disorders",
                             "Psychotic disorders",
                             "Bipolar disorder",
                             "Post traumatic stress disorder",
                             "Autism spectrum disorder",
                             "Attention deficit hyperactivity disorder",
                             "Personality disorders",
                             "Female",
                             "Non-binary/Self-defined",
                             "16-18",
                             "19-25",
                             "36-45",
                             "46-55",
                             "56-65",
                             "66-70",
                             "71-75",
                             "76+",
                             "Mixed or multiple ethnicities",
                             "Asian",
                             "Black",
                             "Other",
                             "Key worker",
                             "Unemployed",
                             "Student",
                             "Retired",
                             "Time between lockdown and baseline")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Gender (Reference male)",
                  "Gender (Reference male)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Employment (Reference: Employed)",
                  "Employment (Reference: Employed)",
                  "Employment (Reference: Employed)",
                  "Employment (Reference: Employed)",
                  "Other")

>>>>

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "Comorbid depression and anxiety",
                             "Depressive disorders",
                             "Anxiety disorders",
                             "Eating disorders",
                             "Obsessive compulsive disorders",
                             "Comorbid psychotic and bipolar disorders",
                             "Psychotic disorders",
                             "Bipolar disorder",
                             "Post traumatic stress disorder",
                             "Autism spectrum disorder",
                             "Attention deficit hyperactivity disorder",
                             "Personality disorders",
                             "Female",
                             "Non-binary/Self-defined",
                             "16-18",
                             "19-25",
                             "36-45",
                             "46-55",
                             "56-65",
                             "66-70",
                             "71-75",
                             "76+",
                             "Mixed or multiple ethnicities",
                             "Asian",
                             "Black",
                             "Other",
                             "Key worker",
                             "Unemployed",
                             "Student",
                             "Retired",
                             "Time between lockdown and baseline")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Gender (Reference male)",
                  "Gender (Reference male)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Other")
